\cvsection{Education}
\cvevent{B.E. (IT) - 9.00 CGPA}{Xavier Institute of Engineering}{ 2020 -- 2024 }{Mumbai, India}{}
% \cvevent{Higher Secondary - 80.8\%}{SD Public School}{ 2019 }{Patel Nagar, Delhi}{}
% \cvevent{Secondary - 10 CGPA }{SD Public School, Patel Nagar, New Delhi}{ 2017 }{Patel Nagar, Delhi}{}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject {\href{https://casecanvas.itsbhanu.com}{Case Canvas}}
\begin{itemize}
\item \textbf{Next.js | Typescript | Framer motion | React-Query | PostgreSQL | Prisma | Stripe} 
\item Built a full-stack SaaS application with a custom product configurator and personalization using canvas manipulation and image processing.
\smallskip
\item Engineered a \textbf{robust backend infrastructure} using PostgreSQL and Prisma, with seamless \textbf{Stripe integration} for secure payments.\
\href{https://github.com/Bhanu1776/CaseCanvas}{Github}
\end{itemize}
\smallskip
\cvproject {\href{https://communisafe.vercel.app}{CommuniSafe}}
\begin{itemize}
\item \textbf{React.js | Node.js | Express.js | MongoDB | Google Maps API | PWA | i18n} 
\item Developed a Progressive Web App (PWA) for disaster management with \textbf{automated alerts}, \textbf{real-time incident reporting} via Google Maps API, and multi-language support (i18n). 
\item Implemented role-based access control and integrated \textbf{GeoLocation}.
\item This resulted in a robust \textbf{Community Resilience Network} that promotes community collaboration and disaster resilience through essential information transmission and efficient response systems. \
\href{https://github.com/Bhanu1776/Community-Resilience-Network}{Github}
\end{itemize}
\smallskip
\cvproject {\href{https://github.com/Bhanu1776/Freelansters}{Freelansters}}
\begin{itemize}
\item \textbf{ReactJs | NodeJs | ExpressJs | MongoDB | Material UI | Styled-Components}
\item Freelansters, a dynamic freelancing platform, streamlines project posting for clients and job searching for freelancers.
\item Advanced \textbf{search filters}, keyword optimization, and sorting functionalities enhance user experience. Ensured security with \textbf{JWT-Auth} for user authentication.
\href{https://github.com/Bhanu1776/Freelansters}{Github}
\end{itemize}
\cvproject{}

\cvsection{Achievements}
\smallskip
\begin{itemize} 

\item Created the \textbf{open-source} \href{https://marketplace.visualstudio.com/items?itemName=Bhanu1776.jellyfish-retro}{jellyfish-x-retro} VS Code theme with \textbf{20,000+} downloads.
\smallskip
\item Published a \textbf{trending} \href{https://starter-website-sigma.vercel.app/}{Nextjs-starter-template} package, garnering attention and adoption within the NPM repository.
\smallskip
\item Achieved a \href{https://www.linkedin.com/posts/bhanu1776_achievementunlocked-gratitude-hackerrank-activity-7178401061966147584-jYYN?utm_source=share&utm_medium=member_desktop}{5-Star Rating} on HackerRank in Problem Solving
\smallskip
\item Secured \textbf{2nd place} out of 25 teams in a \href{https://drive.google.com/file/d/1nK1eTLe6yCUdPNcGmBzwhcu8pcJDxh5a/view?usp=sharing}{hackathon} hosted by SFIT.\\
\end{itemize}
